---
title: "OPEN & REPRODUCIBLE MICROBIOME DATA ANALYSIS SUMMER SCHOOL"   
author: "MolEco WUR"  
---

# Program  



**28th May 2018: Introduction to high-throughput sequencing & tools**    

```{r, echo=FALSE}

tab <- read.table("day1.txt", sep = "\t", header = T)

knitr::kable(tab)

```



**29th May 2018: Day 2	Processing of taxonomic profiling data in R**    

Day 3	Statistical analysis of microbiome composition in R  
8:15- 8:30	Coffee  
8:30 - 9:30	Overview of the central statistical concepts: parametric and non-parametric tests; pairwise and group-wise comparisons; standard and mixed linear models; the role of covariates.  
9:30 - 10:30	Introduction to shot-gun metagenomics.  
10:30 - 10:45	Coffee break  
10:45 - 12:00	Hands-on: univariate tests  
12:00 - 12:30	Lunch break  
12:30 - 15:00	Hands-on: multivariate tests  
15:30 - 16:00 	Coffee break  
16:00 - 17:00	Open discussion forum, review  
17:00	Departure  



**30th May 2018: Day 3	Statistical analysis of microbiome composition in R**    

```{r, echo=FALSE}

tab <- read.table("day2.txt", sep = "\t", header = T)

knitr::kable(tab, align = "l",format = "html")

```



